Comparative Analysis of Lion and AdamW Optimizers for Cross-Encoder Reranking with MiniLM, GTE, and ModernBERT

### 2025-04-26 cross_encoder/paper/main.tex
Modified table structres and added all the available metrices for recall, precision, map etc.

\begin{abstract}
Modern information retrieval systems often employ a two-stage pipeline consisting of an efficient initial retrieval stage followed by a more computationally intensive reranking stage. Cross-encoder models have demonstrated state-of-the-art effectiveness for the reranking task due to their ability to perform deep, contextualized analysis of query-document pairs. The choice of optimizer during the fine-tuning phase can significantly impact the final performance and training efficiency of these models. This paper investigates the impact of using the recently proposed Lion optimizer compared to the widely used AdamW optimizer for fine-tuning cross-encoder rerankers. We fine-tune three distinct transformer models, `microsoft/MiniLM-L12-H384-uncased`, `Alibaba-NLP/gte-multilingual-base`, and `answerdotai/ModernBERT-base`, on the MS MARCO passage ranking dataset using both optimizers. Notably, GTE and ModernBERT support longer context lengths (8192 tokens). The effectiveness of the resulting models is evaluated on the TREC 2019 Deep Learning Track passage ranking task and the MS MARCO development set (for MRR@10). Our experiments, facilitated by the Modal cloud computing platform for GPU resource management, show comparative results across three training epochs. ModernBERT trained with Lion achieved the highest NDCG@10 (0.7225) and MAP (0.5121) on TREC DL 2019, while MiniLM trained with Lion achieved the highest MRR@10 (0.5988) on MS MARCO dev. We analyze the performance trends based on standard IR metrics, providing insights into the relative effectiveness of Lion versus AdamW for different model architectures and training configurations in the context of passage reranking.
\end{abstract}

@@

\begin{table*}[htbp]
\centering
\caption{Evaluation Results on TREC-DL 2019 and MS-MARCO Dev Passage Ranking}
\label{tab:main_results}
\begin{tabular}{l l c c c c c c c}
\toprule
\textbf{Base Model} & \textbf{Optimizer} & \textbf{Epoch} & \textbf{NDCG@10} & \textbf{MAP} & \textbf{MRR@10} & \textbf{Recall@10} & \textbf{R-Prec} & \textbf{P@10} \\
\midrule
\multirow{3}{*}{MiniLM-L12-H384} & \multirow{3}{*}{AdamW}
    & 1 & 0.7008 & 0.4814 & 0.5828 & 0.1712 & 0.4899 & 0.8047 \\
    & & 2 & 0.7094 & 0.4891 & 0.5818 & 0.1715 & 0.5017 & 0.8093 \\
    & & 3 & 0.7127 & 0.4908 & 0.5826 & 0.1706 & 0.4962 & 0.8023 \\
\midrule
\multirow{3}{*}{MiniLM-L12-H384} & \multirow{3}{*}{Lion}
    & 1 & 0.7031 & 0.4858 & 0.5890 & 0.1698 & 0.4904 & 0.8070 \\
    & & 2 & 0.6916 & 0.4755 & 0.5942 & 0.1724 & 0.5041 & 0.8116 \\
    & & 3 & 0.6808 & 0.4706 & \cellcolor{yellow!50}\textbf{0.5988} & 0.1701 & 0.4923 & 0.8023 \\
\midrule
\multirow{3}{*}{GTE-multilingual-base} & \multirow{3}{*}{AdamW}
    & 1 & 0.7224 & 0.5005 & 0.5940 & 0.1733 & 0.4957 & 0.8140 \\
    & & 2 & 0.7203 & 0.4999 & 0.5942 & \cellcolor{yellow!50}\textbf{0.1733} & 0.5067 & 0.8163 \\
    & & 3 & 0.6902 & 0.4899 & 0.5972 & 0.1730 & 0.5069 & 0.8140 \\
\midrule
\multirow{3}{*}{GTE-multilingual-base} & \multirow{3}{*}{Lion}
    & 1 & 0.6785 & 0.4754 & 0.5854 & 0.1684 & 0.4849 & 0.7953 \\
    & & 2 & 0.6909 & 0.4921 & 0.5957 & 0.1721 & 0.5053 & 0.8140 \\
    & & 3 & 0.6904 & 0.4912 & 0.5931 & 0.1719 & 0.5041 & 0.8093 \\
\midrule
\multirow{3}{*}{Modern-BERT-base} & \multirow{3}{*}{AdamW}
    & 1 & 0.7105 & 0.5066 & 0.5865 & 0.1678 & 0.5161 & 0.8163 \\
    & & 2 & 0.6839 & 0.4893 & 0.5885 & 0.1634 & 0.4946 & 0.7814 \\
    & & 3 & 0.6959 & 0.4971 & 0.5916 & 0.1623 & 0.5116 & 0.7860 \\ % Corrected P@10 based on context
\midrule
\multirow{3}{*}{Modern-BERT-base} & \multirow{3}{*}{Lion}
    & 1 & 0.7142 & \cellcolor{yellow!50}\textbf{0.5121} & 0.5834 & 0.1689 & 0.5148 & 0.8163 \\
    & & 2 & \cellcolor{yellow!50}\textbf{0.7225} & 0.5115 & 0.5907 & 0.1732 & \cellcolor{yellow!50}\textbf{0.5183} & 0.8209 \\
    & & 3 & 0.7051 & 0.5020 & \cellcolor{yellow!50}\textbf{0.5988}* & 0.1722 & 0.5102 & \cellcolor{yellow!50}\textbf{0.8256} \\
\bottomrule
\end{tabular}
\vspace{1em}\\
\footnotesize{* MRR@10 is calculated on the MS MARCO v1.1 passage dataset development split. All other metrics are calculated on TREC DL 2019. Best result for each metric highlighted. (*Note: MiniLM+Lion also achieved 0.5988 MRR@10 at epoch 3, (see Appendix A for complete metrics).)}
\end{table*}

@@

\begin{table*}[t]
\centering
\caption{Primary ranking metrics comparing cross-encoder models across training epochs.}
\label{tab:primary_metrics}
\small
\begin{tabular}{llcccccccc}
\toprule
\textbf{Model} & \textbf{Optimizer} & \textbf{Epoch} & \textbf{MAP} & \textbf{NDCG@10} & \textbf{MRR@10} & \textbf{P@10} & \textbf{Recip\_Rank} & \textbf{R-Prec} & \textbf{bpref} \\
\midrule
\multirow{6}{*}{GTE} & \multirow{3}{*}{AdamW} 
 & 1 & 0.5005 & 0.7224 & 0.5940 & 0.8116 & 0.9814 & 0.4964 & 0.6068 \\
 & & 2 & 0.4999 & 0.7203 & 0.5942 & 0.8256 & 0.9523 & 0.5018 & 0.6074 \\
 & & 3 & 0.4899 & 0.6902 & 0.5972 & 0.8093 & 0.9279 & 0.5017 & 0.6075 \\
\cmidrule{2-10}
 & \multirow{3}{*}{Lion} 
 & 1 & 0.4794 & 0.6970 & 0.5854 & 0.7884 & 0.9612 & 0.4814 & 0.6079 \\
 & & 2 & 0.4577 & 0.6792 & 0.5957 & 0.7721 & 0.9477 & 0.4642 & 0.6013 \\
 & & 3 & 0.4521 & 0.6571 & 0.5931 & 0.7488 & 0.9399 & 0.4662 & 0.5972 \\
\midrule
\multirow{6}{*}{MiniLM} & \multirow{3}{*}{AdamW} 
 & 1 & 0.4814 & 0.7008 & 0.5828 & 0.8000 & 0.9465 & 0.4884 & 0.6016 \\
 & & 2 & 0.4891 & 0.7094 & 0.5818 & 0.8116 & 0.9814 & 0.4916 & 0.6030 \\
 & & 3 & 0.4908 & 0.7127 & 0.5826 & 0.8116 & 0.9806 & 0.4943 & 0.6048 \\
\cmidrule{2-10}
 & \multirow{3}{*}{Lion} 
 & 1 & 0.4858 & 0.7031 & 0.5890 & 0.8140 & 0.9457 & 0.4952 & 0.6010 \\
 & & 2 & 0.4755 & 0.6916 & 0.5942 & 0.8070 & 0.9496 & 0.4803 & 0.5992 \\
 & & 3 & 0.4706 & 0.6808 & \textbf{0.5988} & 0.8070 & 0.9419 & 0.4809 & 0.5994 \\
\midrule
\multirow{6}{*}{ModernBERT} & \multirow{3}{*}{AdamW} 
 & 1 & 0.5066 & 0.7105 & 0.5866 & 0.8163 & 0.9574 & 0.5161 & 0.6139 \\
 & & 2 & 0.4893 & 0.6839 & 0.5886 & 0.7814 & 0.9341 & 0.4946 & 0.6152 \\
 & & 3 & 0.4971 & 0.6959 & 0.5916 & 0.7860 & 0.9523 & 0.5116 & 0.6128 \\
\cmidrule{2-10}
 & \multirow{3}{*}{Lion} 
 & 1 & 0.5121 & 0.7142 & 0.5834 & 0.8163 & 0.9593 & 0.5148 & 0.6140 \\
 & & 2 & \textbf{0.5115} & \textbf{0.7225} & 0.5908 & \textbf{0.8209} & \textbf{0.9767} & \textbf{0.5183} & \textbf{0.6156} \\
 & & 3 & 0.5020 & 0.7051 & 0.5989 & 0.8256 & 0.9322 & 0.5102 & 0.6151 \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\centering
\caption{Precision metrics at different cutoff levels.}
\label{tab:precision_metrics}
\small
\begin{tabular}{llccccccc}
\toprule
\textbf{Model} & \textbf{Config} & \textbf{P@5} & \textbf{P@10} & \textbf{P@15} & \textbf{P@20} & \textbf{P@30} & \textbf{P@100} & \textbf{P@200} \\
\midrule
\multirow{6}{*}{GTE} & AdamW-1 & 0.8930 & 0.8116 & 0.7783 & 0.7372 & 0.6419 & 0.3965 & 0.2664 \\
 & AdamW-2 & 0.8698 & 0.8256 & 0.7752 & 0.7326 & 0.6395 & 0.3963 & 0.2641 \\
 & AdamW-3 & 0.8558 & 0.8093 & 0.7550 & 0.7128 & 0.6349 & 0.3942 & 0.2634 \\
 & Lion-1 & 0.8558 & 0.7884 & 0.7364 & 0.7070 & 0.6318 & 0.3893 & 0.2591 \\
 & Lion-2 & 0.8326 & 0.7721 & 0.7302 & 0.6802 & 0.6054 & 0.3740 & 0.2528 \\
 & Lion-3 & 0.8140 & 0.7488 & 0.7147 & 0.6907 & 0.6140 & 0.3740 & 0.2543 \\
\midrule
\multirow{6}{*}{MiniLM} & AdamW-1 & 0.8698 & 0.8000 & 0.7628 & 0.7151 & 0.6450 & 0.3870 & 0.2564 \\
 & AdamW-2 & 0.8698 & 0.8116 & 0.7674 & 0.7186 & 0.6488 & 0.3895 & 0.2580 \\
 & AdamW-3 & 0.8558 & 0.8116 & 0.7705 & 0.7256 & 0.6442 & 0.3891 & 0.2580 \\
 & Lion-1 & 0.8651 & 0.8140 & 0.7783 & 0.7233 & 0.6434 & 0.3847 & 0.2583 \\
 & Lion-2 & 0.8744 & 0.8070 & 0.7643 & 0.7081 & 0.6264 & 0.3821 & 0.2530 \\
 & Lion-3 & 0.8465 & 0.8070 & 0.7442 & 0.6930 & 0.6194 & 0.3809 & 0.2547 \\
\midrule
\multirow{6}{*}{ModernBERT} & AdamW-1 & 0.8651 & 0.8163 & 0.7767 & 0.7349 & 0.6612 & 0.3993 & 0.2679 \\
 & AdamW-2 & 0.8605 & 0.7814 & 0.7333 & 0.6953 & 0.6333 & 0.3912 & 0.2658 \\
 & AdamW-3 & 0.8465 & 0.7860 & 0.7411 & 0.6988 & 0.6450 & 0.3958 & 0.2655 \\
 & Lion-1 & 0.8791 & 0.8163 & 0.7783 & 0.7314 & 0.6574 & 0.4033 & 0.2691 \\
 & Lion-2 & 0.8698 & \textbf{0.8209} & 0.7674 & 0.7279 & 0.6574 & \textbf{0.4016} & 0.2678 \\
 & Lion-3 & 0.8651 & 0.8256 & 0.7504 & 0.7093 & 0.6488 & 0.3967 & 0.2651 \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\centering
\caption{Recall metrics at different cutoff levels.}
\label{tab:recall_metrics}
\small
\begin{tabular}{llcccccccc}
\toprule
\textbf{Model} & \textbf{Config} & \textbf{Recall@5} & \textbf{Recall@10} & \textbf{Recall@15} & \textbf{Recall@20} & \textbf{Recall@30} & \textbf{Recall@100} & \textbf{Recall@200} & \textbf{Recall@500} \\
\midrule
\multirow{6}{*}{GTE} & AdamW-1 & 0.1051 & 0.1689 & 0.2286 & 0.2815 & 0.3376 & 0.5501 & 0.6573 & 0.7161 \\
 & AdamW-2 & 0.1041 & 0.1760 & 0.2295 & 0.2753 & 0.3366 & 0.5538 & 0.6511 & 0.7130 \\
 & AdamW-3 & 0.1051 & 0.1715 & 0.2256 & 0.2692 & 0.3376 & 0.5489 & 0.6501 & 0.7102 \\
 & Lion-1 & 0.1002 & 0.1614 & 0.2158 & 0.2684 & 0.3369 & 0.5401 & 0.6384 & 0.7101 \\
 & Lion-2 & 0.0973 & 0.1610 & 0.2151 & 0.2545 & 0.3153 & 0.5211 & 0.6273 & 0.7105 \\
 & Lion-3 & 0.0929 & 0.1542 & 0.2070 & 0.2574 & 0.3221 & 0.5181 & 0.6227 & 0.7124 \\
\midrule
\multirow{6}{*}{MiniLM} & AdamW-1 & 0.1027 & 0.1652 & 0.2225 & 0.2645 & 0.3362 & 0.5426 & 0.6396 & 0.7187 \\
 & AdamW-2 & 0.1013 & 0.1668 & 0.2239 & 0.2676 & 0.3401 & 0.5446 & 0.6417 & 0.7223 \\
 & AdamW-3 & 0.1007 & 0.1702 & 0.2257 & 0.2719 & 0.3386 & 0.5427 & 0.6396 & 0.7189 \\
 & Lion-1 & 0.1022 & 0.1688 & 0.2257 & 0.2704 & 0.3400 & 0.5338 & 0.6413 & 0.7154 \\
 & Lion-2 & 0.1025 & 0.1641 & 0.2200 & 0.2613 & 0.3289 & 0.5338 & 0.6268 & 0.7145 \\
 & Lion-3 & 0.1001 & 0.1676 & 0.2156 & 0.2542 & 0.3253 & 0.5249 & 0.6341 & 0.7143 \\
\midrule
\multirow{6}{*}{ModernBERT} & AdamW-1 & 0.0995 & 0.1678 & 0.2245 & 0.2731 & 0.3475 & 0.5520 & 0.6539 & 0.7224 \\
 & AdamW-2 & 0.0979 & 0.1634 & 0.2148 & 0.2603 & 0.3321 & 0.5443 & 0.6520 & 0.7198 \\
 & AdamW-3 & 0.1019 & 0.1623 & 0.2184 & 0.2627 & 0.3380 & 0.5476 & 0.6461 & 0.7198 \\
 & Lion-1 & 0.1052 & 0.1689 & 0.2276 & 0.2733 & 0.3431 & 0.5542 & 0.6553 & 0.7233 \\
 & Lion-2 & 0.1048 & \textbf{0.1732} & 0.2245 & 0.2699 & 0.3469 & \textbf{0.5608} & \textbf{0.6553} & \textbf{0.7233} \\
 & Lion-3 & 0.1037 & 0.1722 & 0.2185 & 0.2640 & 0.3425 & 0.5570 & 0.6525 & 0.7194 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{abstract}
Modern information retrieval systems often employ a two-stage pipeline consisting of an efficient initial retrieval stage followed by a more computationally intensive reranking stage. Cross-encoder models have demonstrated state-of-the-art effectiveness for the reranking task due to their ability to perform deep, contextualized analysis of query-document pairs. The choice of optimizer during the fine-tuning phase can significantly impact the final performance and training efficiency of these models. This paper investigates the impact of using the recently proposed Lion optimizer compared to the widely used AdamW optimizer for fine-tuning cross-encoder rerankers. We fine-tune three distinct transformer models, `microsoft/MiniLM-L12-H384-uncased`, `Alibaba-NLP/gte-multilingual-base`, and `answerdotai/ModernBERT-base`, on the MS MARCO passage ranking dataset using both optimizers. Notably, GTE and ModernBERT support longer context lengths (8192 tokens). The effectiveness of the resulting models is evaluated on the TREC 2019 Deep Learning Track passage ranking task and the MS MARCO development set (for MRR@10). Our experiments, facilitated by the Modal cloud computing platform for GPU resource management, show comparative results across three training epochs. ModernBERT trained with Lion achieved the highest NDCG@10 (0.7225) and MAP (0.5121) on TREC DL 2019, while MiniLM trained with Lion tied with ModernBERT with Lion on MRR@10 (0.5988) on MS MARCO dev. We analyze the performance trends based on standard IR metrics, providing insights into the relative effectiveness of Lion versus AdamW for different model architectures and training configurations in the context of passage reranking.
\end{abstract}

@@

\begin{table*}[htbp]
\centering
\caption{Evaluation Results on TREC-DL 2019 and MS-MARCO Dev Passage Ranking}
\label{tab:main_results}
\begin{tabular}{l l c c c c c c c}
\toprule
\textbf{Base Model} & \textbf{Optimizer} & \textbf{Epoch} & \textbf{NDCG@10} & \textbf{MAP} & \textbf{MRR@10} & \textbf{Recall@10} & \textbf{R-Prec} & \textbf{P@10} \\
\midrule
\multirow{3}{*}{MiniLM-L12-H384} & \multirow{3}{*}{AdamW}
    & 1 & 0.7008 & 0.4814 & 0.5828 & 0.1712 & 0.4899 & 0.8047 \\
    & & 2 & 0.7094 & 0.4891 & 0.5818 & 0.1715 & 0.5017 & 0.8093 \\
    & & 3 & 0.7127 & 0.4908 & 0.5826 & 0.1706 & 0.4962 & 0.8023 \\
\midrule
\multirow{3}{*}{MiniLM-L12-H384} & \multirow{3}{*}{Lion}
    & 1 & 0.7031 & 0.4858 & 0.5890 & 0.1698 & 0.4904 & 0.8070 \\
    & & 2 & 0.6916 & 0.4755 & 0.5942 & 0.1724 & 0.5041 & 0.8116 \\
    & & 3 & 0.6808 & 0.4706 & \cellcolor{yellow!50}\textbf{0.5988} & 0.1701 & 0.4923 & 0.8023 \\
\midrule
\multirow{3}{*}{GTE-multilingual-base} & \multirow{3}{*}{AdamW}
    & 1 & 0.7224 & 0.5005 & 0.5940 & 0.1733 & 0.4957 & 0.8140 \\
    & & 2 & 0.7203 & 0.4999 & 0.5942 & \cellcolor{yellow!50}\textbf{0.1733} & 0.5067 & 0.8163 \\
    & & 3 & 0.6902 & 0.4899 & 0.5972 & 0.1730 & 0.5069 & 0.8140 \\
\midrule
\multirow{3}{*}{GTE-multilingual-base} & \multirow{3}{*}{Lion}
    & 1 & 0.6785 & 0.4754 & 0.5854 & 0.1684 & 0.4849 & 0.7953 \\
    & & 2 & 0.6909 & 0.4921 & 0.5957 & 0.1721 & 0.5053 & 0.8140 \\
    & & 3 & 0.6904 & 0.4912 & 0.5931 & 0.1719 & 0.5041 & 0.8093 \\
\midrule
\multirow{3}{*}{Modern-BERT-base} & \multirow{3}{*}{AdamW}
    & 1 & 0.7105 & 0.5066 & 0.5865 & 0.1678 & 0.5161 & 0.8163 \\
    & & 2 & 0.6839 & 0.4893 & 0.5885 & 0.1634 & 0.4946 & 0.7814 \\
    & & 3 & 0.6959 & 0.4971 & 0.5916 & 0.1623 & 0.5116 & 0.7860 \\ % Corrected P@10 based on context
\midrule
\multirow{3}{*}{Modern-BERT-base} & \multirow{3}{*}{Lion}
    & 1 & 0.7142 & \cellcolor{yellow!50}\textbf{0.5121} & 0.5834 & 0.1689 & 0.5148 & 0.8163 \\
    & & 2 & \cellcolor{yellow!50}\textbf{0.7225} & 0.5115 & 0.5907 & 0.1732 & \cellcolor{yellow!50}\textbf{0.5183} & 0.8209 \\
    & & 3 & 0.7051 & 0.5020 & \cellcolor{yellow!50}\textbf{0.5988}* & 0.1722 & 0.5102 & \cellcolor{yellow!50}\textbf{0.8256} \\
\bottomrule
\end{tabular}
\vspace{1em}\\
\footnotesize{* MRR@10 is calculated on the MS MARCO v1.1 passage dataset development split. All other metrics are calculated on TREC DL 2019. Best result for each metric highlighted. (*Note: MiniLM+Lion also achieved 0.5988 MRR@10 at epoch 3, (see \autoref{app:metrics} for complete metrics).)}
\end{table*}

@@

\begin{table*}[t]
\centering
\caption{Primary ranking metrics comparing cross-encoder models across training epochs.}
\label{tab:primary_metrics}
\small
\begin{tabular}{llcccccccc}
\toprule
\textbf{Model} & \textbf{Optimizer} & \textbf{Epoch} & \textbf{MAP} & \textbf{NDCG@10} & \textbf{MRR@10} & \textbf{P@10} & \textbf{Recip\_Rank} & \textbf{R-Prec} & \textbf{bpref} \\
\midrule
\multirow{6}{*}{GTE} & \multirow{3}{*}{AdamW} 
 & 1 & 0.5005 & 0.7224 & 0.5940 & 0.8116 & \textbf{0.9814} & 0.4964 & 0.6068 \\
 & & 2 & 0.4999 & 0.7203 & 0.5942 & \textbf{0.8256} & 0.9523 & 0.5018 & 0.6074 \\
 & & 3 & 0.4899 & 0.6902 & 0.5972 & 0.8093 & 0.9279 & 0.5017 & 0.6075 \\
\cmidrule{2-10}
 & \multirow{3}{*}{Lion} 
 & 1 & 0.4794 & 0.6970 & 0.5854 & 0.7884 & 0.9612 & 0.4814 & 0.6079 \\
 & & 2 & 0.4577 & 0.6792 & 0.5957 & 0.7721 & 0.9477 & 0.4642 & 0.6013 \\
 & & 3 & 0.4521 & 0.6571 & 0.5931 & 0.7488 & 0.9399 & 0.4662 & 0.5972 \\
\midrule
\multirow{6}{*}{MiniLM} & \multirow{3}{*}{AdamW} 
 & 1 & 0.4814 & 0.7008 & 0.5828 & 0.8000 & 0.9465 & 0.4884 & 0.6016 \\
 & & 2 & 0.4891 & 0.7094 & 0.5818 & 0.8116 & \textbf{0.9814} & 0.4916 & 0.6030 \\
 & & 3 & 0.4908 & 0.7127 & 0.5826 & 0.8116 & 0.9806 & 0.4943 & 0.6048 \\
\cmidrule{2-10}
 & \multirow{3}{*}{Lion} 
 & 1 & 0.4858 & 0.7031 & 0.5890 & 0.8140 & 0.9457 & 0.4952 & 0.6010 \\
 & & 2 & 0.4755 & 0.6916 & 0.5942 & 0.8070 & 0.9496 & 0.4803 & 0.5992 \\
 & & 3 & 0.4706 & 0.6808 & \textbf{0.5988} & 0.8070 & 0.9419 & 0.4809 & 0.5994 \\
\midrule
\multirow{6}{*}{ModernBERT} & \multirow{3}{*}{AdamW} 
 & 1 & 0.5066 & 0.7105 & 0.5866 & 0.8163 & 0.9574 & 0.5161 & 0.6139 \\
 & & 2 & 0.4893 & 0.6839 & 0.5886 & 0.7814 & 0.9341 & 0.4946 & 0.6152 \\
 & & 3 & 0.4971 & 0.6959 & 0.5916 & 0.7860 & 0.9523 & 0.5116 & 0.6128 \\
\cmidrule{2-10}
 & \multirow{3}{*}{Lion} 
 & 1 & \textbf{0.5121} & 0.7142 & 0.5834 & 0.8163 & 0.9593 & 0.5148 & 0.6140 \\
 & & 2 & 0.5115 & \textbf{0.7225} & 0.5908 & 0.8209 & 0.9767 & \textbf{0.5183} & \textbf{0.6156} \\
 & & 3 & 0.5020 & 0.7051 & \textbf{0.5988} & \textbf{0.8256} & 0.9322 & 0.5102 & 0.6151 \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
\centering
\caption{Precision metrics at different cutoff levels.}
\label{tab:precision_metrics}
\small
\begin{tabular}{llcccccccccc}
\toprule
\textbf{Model} & \textbf{Optimizer} & \textbf{Epoch} & \textbf{P@5} & \textbf{P@10} & \textbf{P@15} & \textbf{P@20} & \textbf{P@30} & \textbf{P@100} & \textbf{P@200} & \textbf{P@500} & \textbf{P@1000}\\
\midrule
\multirow{6}{*}{GTE} & \multirow{3}{*}{AdamW} 
 & 1 & 0.8930 & 0.8116 & 0.7783 & 0.7372 & 0.6419 & 0.3965 & 0.2664 & 0.1238 & 0.0654 \\
 & & 2 & 0.8698 & 0.8256 & 0.7752 & 0.7326 & 0.6395 & 0.3963 & 0.2641 & 0.1230 & 0.0654 \\
 & & 3 & 0.8558 & 0.8093 & 0.7550 & 0.7128 & 0.6349 & 0.3942 & 0.2634 & 0.1225 & 0.0654 \\
\cmidrule{2-12}
 & \multirow{3}{*}{Lion} 
 & 1 & 0.8558 & 0.7884 & 0.7364 & 0.7070 & 0.6318 & 0.3893 & 0.2591 & 0.1228 & 0.0654 \\
 & & 2 & 0.8326 & 0.7721 & 0.7302 & 0.6802 & 0.6054 & 0.3740 & 0.2528 & 0.1227 & 0.0654 \\
 & & 3 & 0.8140 & 0.7488 & 0.7147 & 0.6907 & 0.6140 & 0.3740 & 0.2543 & 0.1231 & 0.0654 \\
\midrule
\multirow{6}{*}{MiniLM} & \multirow{3}{*}{AdamW} 
 & 1 & 0.8698 & 0.8000 & 0.7628 & 0.7151 & 0.6450 & 0.3870 & 0.2564 & 0.1242 & 0.0654 \\
 & & 2 & 0.8698 & 0.8116 & 0.7674 & 0.7186 & 0.6488 & 0.3895 & 0.2580 & 0.1247 & 0.0654 \\
 & & 3 & 0.8558 & 0.8116 & 0.7705 & 0.7256 & 0.6442 & 0.3891 & 0.2580 & 0.1245 & 0.0654 \\
\cmidrule{2-12}
 & \multirow{3}{*}{Lion} 
 & 1 & 0.8651 & 0.8140 & 0.7783 & 0.7233 & 0.6434 & 0.3847 & 0.2583 & 0.1242 & 0.0654 \\
 & & 2 & 0.8744 & 0.8070 & 0.7643 & 0.7081 & 0.6264 & 0.3821 & 0.2530 & 0.1240 & 0.0654 \\
 & & 3 & 0.8465 & 0.8070 & 0.7442 & 0.6930 & 0.6194 & 0.3809 & 0.2547 & 0.1240 & 0.0654 \\
\midrule
\multirow{6}{*}{ModernBERT} & \multirow{3}{*}{AdamW} 
 & 1 & 0.8651 & 0.8163 & 0.7767 & 0.7349 & 0.6612 & 0.3993 & 0.2679 & 0.1262 & 0.0654\\
 & & 2 & 0.8605 & 0.7814 & 0.7333 & 0.6953 & 0.6333 & 0.3912 & 0.2658 & 0.1257 & 0.0654 \\
 & & 3 & 0.8465 & 0.7860 & 0.7411 & 0.6988 & 0.6450 & 0.3958 & 0.2655 & 0.1253 & 0.0654 \\
\cmidrule{2-12}
 & \multirow{3}{*}{Lion} 
 & 1 & 0.8791 & 0.8163 & 0.7783 & 0.7314 & 0.6574 & 0.4033 & 0.2691 & 0.1265 & 0.0654\\
 & & 2 & 0.8698 & \textbf{0.8209} & 0.7674 & 0.7279 & 0.6574 & \textbf{0.4016} & 0.2678 & 0.1267 & 0.0654\\
 & & 3 & 0.8651 & 0.8256 & 0.7504 & 0.7093 & 0.6488 & 0.3967 & 0.2651 & 0.1263 & 0.0654 \\
\bottomrule
\end{tabular}
\end{table*}

% \begin{table*}[t]
% \centering
% \caption{Precision metrics at different cutoff levels.}
% \label{tab:precision_metrics}
% \small
% \begin{tabular}{llccccccc}
% \toprule
% \textbf{Model} & \textbf{Config} & \textbf{P@5} & \textbf{P@10} & \textbf{P@15} & \textbf{P@20} & \textbf{P@30} & \textbf{P@100} & \textbf{P@200} \\
% \midrule
% \multirow{6}{*}{GTE} & AdamW-1 & 0.8930 & 0.8116 & 0.7783 & 0.7372 & 0.6419 & 0.3965 & 0.2664 \\
%  & AdamW-2 & 0.8698 & 0.8256 & 0.7752 & 0.7326 & 0.6395 & 0.3963 & 0.2641 \\
%  & AdamW-3 & 0.8558 & 0.8093 & 0.7550 & 0.7128 & 0.6349 & 0.3942 & 0.2634 \\
%  & Lion-1 & 0.8558 & 0.7884 & 0.7364 & 0.7070 & 0.6318 & 0.3893 & 0.2591 \\
%  & Lion-2 & 0.8326 & 0.7721 & 0.7302 & 0.6802 & 0.6054 & 0.3740 & 0.2528 \\
%  & Lion-3 & 0.8140 & 0.7488 & 0.7147 & 0.6907 & 0.6140 & 0.3740 & 0.2543 \\
% \midrule
% \multirow{6}{*}{MiniLM} & AdamW-1 & 0.8698 & 0.8000 & 0.7628 & 0.7151 & 0.6450 & 0.3870 & 0.2564 \\
%  & AdamW-2 & 0.8698 & 0.8116 & 0.7674 & 0.7186 & 0.6488 & 0.3895 & 0.2580 \\
%  & AdamW-3 & 0.8558 & 0.8116 & 0.7705 & 0.7256 & 0.6442 & 0.3891 & 0.2580 \\
%  & Lion-1 & 0.8651 & 0.8140 & 0.7783 & 0.7233 & 0.6434 & 0.3847 & 0.2583 \\
%  & Lion-2 & 0.8744 & 0.8070 & 0.7643 & 0.7081 & 0.6264 & 0.3821 & 0.2530 \\
%  & Lion-3 & 0.8465 & 0.8070 & 0.7442 & 0.6930 & 0.6194 & 0.3809 & 0.2547 \\
% \midrule
% \multirow{6}{*}{ModernBERT} & AdamW-1 & 0.8651 & 0.8163 & 0.7767 & 0.7349 & 0.6612 & 0.3993 & 0.2679 \\
%  & AdamW-2 & 0.8605 & 0.7814 & 0.7333 & 0.6953 & 0.6333 & 0.3912 & 0.2658 \\
%  & AdamW-3 & 0.8465 & 0.7860 & 0.7411 & 0.6988 & 0.6450 & 0.3958 & 0.2655 \\
%  & Lion-1 & 0.8791 & 0.8163 & 0.7783 & 0.7314 & 0.6574 & 0.4033 & 0.2691 \\
%  & Lion-2 & 0.8698 & \textbf{0.8209} & 0.7674 & 0.7279 & 0.6574 & \textbf{0.4016} & 0.2678 \\
%  & Lion-3 & 0.8651 & 0.8256 & 0.7504 & 0.7093 & 0.6488 & 0.3967 & 0.2651 \\
% \bottomrule
% \end{tabular}
% \end{table*}
